To Do List

### 2018-11-14 ToDo.Rmd
updates

>>>>

## 10/03/18

* pose additional question, does doing multiple iterations of sampling improve model performance
* can we prove that the performance (f1 score & variables selected) is stable over multiple iterations

## 10/05/18

* does random forest sufffer on imbalanced data?
* use maximum instead of mean when determining cutoff of iterations
* find out if there is a convergence algorthim to decide point of convergence
   + look at 0.001 or 0.0001 for now
* look at AIC/BIC for potential cutoff
* run anova test to determine if two models are different at different iterations
* look into using c-index as performance metric
* create heatmap of variable importance from different models

## 11/09/18

*stick with elastic net (compare with all others)
*look at correlations
